---
title: "590D-Mini Exercise-1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reservoir Sampling

**Task**
Implement reservoir sampling when reservoir has size 1. Let the items from 1 to 100 appear one by one.

* Report the item sampled in one run of the algorithm.
* Repeat the algorithm for 1000 times and plot the
number of times each element is selected.
* Repeat the algorithm for 10000 times and plot the number of times each element is selected.
* Repeat the algorithm for 100000 times and plot the number of times each element is selected.

**Solution**

```{r}
resSample <- function(n){
  resv <- integer()
  counter <- vector(mode = "integer", length = 100)
  
  #N Runs of Algorithm
  for (i in 1:n){
    
    #Reservoir Sampling Algorithm (with reservoir= 1)
    for(i in 1:100){
      x <- i
      probability <- c(1/i, 1-1/i)
      decision <- sample(c(T,F), 1, prob = probability)
      switch(decision, resv <- x)
    }
    counter[[resv]] = counter[[resv]] + 1
  }
  
  if(n == 1)
    print(resv)
  else
    plot(counter, type = "l", col = "dark red")
}
```

* **Reporting item for one algorithm run**:

```{r }
resSample(1)
```

* **Plot for 1000 algorithm runs**:

```{r}
resSample(1000)
```

* **Plot for 10000 algorithm runs**:

```{r}
resSample(10000)
```

* **Plot for 100000 algorithm runs**:

```{r}
resSample(100000)
```

*by Aditya Agrawal*